Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-07-23 paper/main.tex
paper outline

\emph{(Data pipeline summary)} Our raw data consist of every Python 3 program
that a user executed on PythonTutor.com (not in "live" mode) during 2017, which
comes to around 5 million programs. Each program which crashes is paired with
the next program (by the same user) that does not crash. We discard pairs where the
difference between crashing and fixed versions is too high (more than a stddev
above average).

@@

\item \emph{Dynamic features}
We run each program through an instrumented interpreter (i.e. a modified PythonTutor
backend, which itself is based on the BDB debugging library). This lets us
compute the following features:
\begin{enumerate}
    \item What type(s) does the expression have at runtime?
    \item Is it part of the error slice?
\end{enumerate}
(Since this interpreter works at the granularity of lines and we want to work with
expressions as well, we first convert each program to ANF.)

@@

We also check what exception is thrown (TypeError, KeyError, etc), and add that
as a feature to all vectors derived from that program.

>>>>

\emph{(Data pipeline summary)} Our raw data consist of every Python 3 program
that a user executed on PythonTutor.com (not in "live" mode) during 2017, other
than those with syntax errors or undefined variables. Each program which crashes
(throws an uncaught Python exception) is paired with
the next program (by the same user) that does not crash, under the assumption
that the latter is the fixed version of the former. We discard pairs where the
difference between crashing and fixed versions is too high (more than a stddev
above average), since these are most likely to be violations of that
assumption (i.e. the program that does not crash is unrelated to the crashing
program).

@@

\item \emph{Dynamic features}
We run each program through an instrumented interpreter (i.e. a modified PythonTutor
backend, which itself is based on the BDB debugging library). This lets us
compute the following features:
\begin{enumerate}
    \item What type(s) does the expression have at runtime? (The values of this feature
    can be a type like int, or the special values "unknown" if the expression is
    never successfully evaluated and "multiple" if it changes type.)
    \item Is it part of the error slice?
    \item Is it the node at which the program actually crashes?
\end{enumerate}
(Since this interpreter works at the granularity of lines and we want to work with
expressions as well, we first convert each program to ANF.)

@@

We also check what uncaught exception is thrown by the program (TypeError,
KeyError, etc), and add that as a constant feature to all vectors derived from that program.
